\textbf{COMP0078 Assignment 2}

### 2022-11-30 submission.tex
pretty pictures added

\begin{document}
    \maketitle
\section{PART I}
\subsection{Kerenl Perceptron}
\newpage
\section{PART II}
\subsection{Semi-supervised Leanrning via Laplacian Interpolation}
\newpage
\section{PART III}
\subsection{Questions}
\begin{itemize}
    \item[1.]
    \item[2.]
    \item[3.]
\end{itemize}
\end{document}

>>>>

\begin{document}
    \maketitle
\section{PART I}
\subsection{Kernel Perceptron}
\newpage
\section{PART II}
\subsection{Semi-supervised Leanrning via Laplacian Interpolation}
Experimental report for the laplacian interpolation approach:
\\

\includegraphics{outputs/part2/laplacian_interpolation_report.png}

\\

And for the laplacian kernel method:

\includegraphics{outputs/part2/laplacian_kernel_interpolation_report.png}

\newpage

\section{PART III}
\subsection{Questions}
\begin{itemize}
    \item[1.]
    \item[2.]
    \item[3.]
\end{itemize}
\end{document}
